### 2022-05-01 bms/bezdratove_lokalni_site/bezdratove_lokalni_site.tex
update naming

% VUT FIT MITAI
% MSZ 2021/2022
% Author: Vladimir Dusek
% Login: xdusek27

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\chapter{BMS -- Bezdrátové lokální sítě (Wifi, Bluetooth).}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Metadata}

\begin{compactitem}
    \item Předmět: Bezdrátové a mobilní sítě (BMS)
    \item Přednáška:
    \begin{compactitem}
        \item \todo{todo}
    \end{compactitem}
    \item Záznam:
    \begin{compactitem}
        \item \todo{todo}
    \end{compactitem}
\end{compactitem}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Úvod a kontext}

\todo{todo}